---
title: "Session 1.2"
subtitle: "Global Health Research"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```


## Before Class

Some text to introduce the session/chapter. You will learn: 

* LO1
* LO2
* LO3
* LO4

Here's what you should do to prepare for class:

* Read [Chapter 2](http://themethodsection.com/ebook/ghr.html) and complete the reading assessment at the end of the chapter
* Watch the video
* Complete the activity prep

## Watch

![](https://youtu.be/zNzZ1PfUDNk)

## Activity Prep

Background on activity here. The goal of this activity is to ABC.

Here's what you should do to before class to prepare:

* Read study X
* Read study Y
* Complete the following activity readiness questions

### Activity Readiness Questions

```{r quiz}
quiz(
  question("Which package contains functions for installing other R packages?",
    answer("base"),
    answer("tools"),
    answer("utils", correct = TRUE),
    answer("codetools")
  ),
  question("Which of the R packages listed below are used to create plots?",
    answer("lattice", correct = TRUE),
    answer("tools"),
    answer("stats"),
    answer("grid", correct = TRUE)
  )
)
```


## In-Class Activity

*Here's a simple exercise with an empty code chunk provided for entering the answer.*

Write the R code required to add two plus two:

```{r two-plus-two, exercise=TRUE}

```

### Exercise with Code

*Here's an exercise with some prepopulated code as well as `exercise.lines = 5` to provide a bit more initial room to work.*

Now write a function that adds any two numbers and then call it:

```{r add-function, exercise=TRUE, exercise.lines = 5}
add <- function() {
  
}
```

